% Meyers_Chris_Resume.tex

\input{Meyers_Chris_Settings}

\begin{document}

% =================================== Header ===================================
\input{Meyers_Chris_Header}

% ================================= Experience =================================
\hrule
\vspace{-0.4em}
\subsection*{Experience}

\begin{itemize}
  \parskip=0.1em

% BEGIN Experience
  \item
  \headerrow
    {\textbf{MCG Strategic}}
    {\textbf{Marlton, NJ}}
  \\
  \headerrow
    {\emph{Software Engineer}}
    {\emph{Feb 2017 -- Present}}
  \begin{itemize*}
    \item Lead backend developer and maintainer of client websites, web apps, and mobile apps.
    \item Contributed to the creation of engineering process best practices to strengthen development and QA workflow.
    \item Designed and implemented automation tools that include an app build/delivery system and a weekly time report generation system.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{ASRC Federal Mission Solutions}}
    {\textbf{Moorestown, NJ}}
  \\
  \headerrow
    {\emph{Software Engineer, Display Systems}}
    {\emph{May 2015 -- Feb 2017}}
  \begin{itemize*}
    \item Designed, developed, and tested solutions in CMMI Level 5 for the U.S. Navy's real-time, \break mission critical Aegis Ballistic Missile Defense (BMD) system.
    \item Nominated as a mentor to help new employees adjust to their position.
    \item Lead developer of the display component for the Littoral Combat Ship's (LCS) SeaRAM weapon system.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{ASRC Federal Mission Solutions}}
    {\textbf{Moorestown, NJ}}
  \\
  \headerrow
    {\emph{Software Engineer Intern, Display Systems}}
    {\emph{Mar 2015 -- May 2015}}
  \begin{itemize*}
    \item Assisted a team working on the Aegis Ballistic Missile Defense (BMD) system.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Rowan University, History Department}}
    {\textbf{Glassboro, NJ}}
  \\
  \headerrow
    {\emph{Web Developer}}
    {\emph{Nov 2013 -- May 2015}}
  \begin{itemize*}
    \item Updated and maintained the History Department's website.
  \end{itemize*}

  \item
  \headerrow
    {\textbf{Rowan University, Network \& System Services}}
    {\textbf{Glassboro, NJ}}
  \\
  \headerrow
    {\emph{Network Assistant}}
    {\emph{Jul 2014 -- Sept 2014}}
  \begin{itemize*}
    \item Installed and maintained network infrastructure across the Glassboro campus.
  \end{itemize*}
% END Experience

\end{itemize}

% ================================== Education =================================
\hrule
\vspace{-0.4em}
\subsection*{Education}

\begin{itemize}
  \parskip=0.1em

% BEGIN Education
  \item 
  \headerrow
    {\textbf{Rowan University}}
    {\textbf{Glassboro, NJ}}
  \\
  \headerrow
    {\emph{Bachelor of Science, Computer Science}}
    {\emph{Sept 2011 -- May 2015}}
% END Education

\end{itemize}

% ============================== Technical Skills ==============================
\hrule
\vspace{-0.4em}
\subsection*{Technical Skills}

\begin{itemize*}
% BEGIN TechnicalSkills
  \item Experience developing various software using languages such as \CPP, Java, and C\#.
  \item Experience developing websites and web apps using languages and technologies such as the LAMP stack (Linux, Apache, MySQL, PHP), Flask (Python web framework), and JavaScript.
  \item Experience developing native Android apps and hybrid mobile apps with Apache Cordova.
  \item Experience with concrete5, WordPress, and Drupal Content Management Systems (CMSs).
  \item Experience writing Bash and Python scripts to automate processes and aid in development.
  \item Experience as a member of Agile and Kanban teams utilizing JIRA to track issues.
  \item Experience with Git, ClearCase, and Subversion version control.
  \item Experience debugging software with visual debuggers and the command line GNU debugger (GDB).
  \item Very comfortable with Windows, macOS, and Command Line Interfaces (Unix, Linux, Solaris).
  \item Experience installing, maintaining, and relocating data center hardware.
% END TechnicalSkills
\end{itemize*}

\end{document}
